\cvsection{Experience}
\begin{cventries}
    \cventry
    {Web Crawling Team}
    {Bloomberg Software Engineering Intern}
    {Princeton, New Jersey}
    {May 2017 - July 2017}
    {
      \begin{cvitems}
        \item {Improved proactive identification of problems with the web crawling system by publishing metrics to a telemetry system and developing and deploying a system dashboard.}
        \item {Decreased time needed to detect system problems by visualizing this metrics data on the time series analytics platform Grafana.}
        \item {Simplified system maintenance by publishing metrics in an easily extendable way.}
        \item {Wrote the frontend with Angular.js and developed the backend in Cython and Python.}
      \end{cvitems} 
    }
  \cventry
    {Researcher for <Developing Networking for a Real-Time Mobile Gaze Tracker>}
    {Research Assistant, Sensors Lab (Prof. Deepak Ganesan)}
    {Amherst, Massachusetts}
    {June 2016 - PRESENT}
    {
      \begin{cvitems}
        \item {Implemented Bluetooth file transfer for the iShadow wearable gaze tracker by writing a server program on the embedded device and a client app for Android.}
        \item {Dropped less than 1\% of packets, even at a distance of several meters.} 
      \end{cvitems} 
    }
     \cventry
    {Course Staff}
    {Undergraduate Course Assistant for COMPSCI 190D}
    {Amherst, Massachusetts}
    {September 2016 - PRESENT}
    {
      \begin{cvitems}
        \item {Graded assignments for an introductory computer science course in Java.}
      \end{cvitems} 
    }
  
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
\end{cventries}
